quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-12 paper-quollr.Rmd
Added generate hexgonal centroids

>>>>

The `gen_centroids()` function calculates the centroids of a hexagonal grid.

The coordinate limits of the embedding (`lim1` and `lim2`) are used to compute the aspect ratio between the two axes, which informs vertical spacing. The function then calls `calc_bins_y()`, a helper function that determines the appropriate number of hexagonal rows (`bin2`) and the width of each hexagon (`a1`) given the specified number of bins along the x-axis (`bin1`) and buffer (`q`).

Then, the centroids are computed iteratively. The x-coordinates for centroids in odd-numbered rows are initialized as a sequence spaced by the hexagon width. Even-numbered rows are staggered by half this width to achieve a hexagonal tiling effect. Vertical spacing (`a2`) is derived by $\sqrt{3}/2 \times a_1$.

The y-coordinates for each row are similarly calculated, and paired with the x-coordinates based on whether the total number of rows is even or odd. In the case of an odd number of rows, the final row uses only the odd-row x-coordinates to maintain the alternating pattern.

Finally, a tibble is returned containing a unique hexagon ID (`hexID`) along with the corresponding x and y centroid coordinates (`c_x`, `c_y`), which define the layout of the hexagonal grid over the $2-\text{D}$ space.

### 2025-05-12 paper-quollr.tex
Added generate hexgonal centroids

>>>>

The \texttt{gen\_centroids()} function calculates the centroids of a hexagonal grid.

The coordinate limits of the embedding (\texttt{lim1} and \texttt{lim2}) are used to compute the aspect ratio between the two axes, which informs vertical spacing. The function then calls \texttt{calc\_bins\_y()}, a helper function that determines the appropriate number of hexagonal rows (\texttt{bin2}) and the width of each hexagon (\texttt{a1}) given the specified number of bins along the x-axis (\texttt{bin1}) and buffer (\texttt{q}).

Then, the centroids are computed iteratively. The x-coordinates for centroids in odd-numbered rows are initialized as a sequence spaced by the hexagon width. Even-numbered rows are staggered by half this width to achieve a hexagonal tiling effect. Vertical spacing (\texttt{a2}) is derived by \(\sqrt{3}/2 \times a_1\).

The y-coordinates for each row are similarly calculated, and paired with the x-coordinates based on whether the total number of rows is even or odd. In the case of an odd number of rows, the final row uses only the odd-row x-coordinates to maintain the alternating pattern.

Finally, a tibble is returned containing a unique hexagon ID (\texttt{hexID}) along with the corresponding x and y centroid coordinates (\texttt{c\_x}, \texttt{c\_y}), which define the layout of the hexagonal grid over the \(2-\text{D}\) space.
